Quantum Hoare Type Theory

### 2020-10-01 ms-paper/ms-paper.tex
Add city
Add implementation notes and citations

\author{Kartik Singhal}
\orcid{0000-0003-1132-269X}
\affiliation{
	\position{PhD Student}
	\department{Department of Computer Science}
	\institution{University of Chicago}
	\state{IL}
%	\postcode{60637}
	\country{USA}}
\email{ks@cs.uchicago.edu}

@@

>>>>

\author{Kartik Singhal}
\orcid{0000-0003-1132-269X}
\affiliation{
	\position{PhD Student}
	\department{Department of Computer Science}
	\institution{University of Chicago}
	\city{Chicago}
	\state{IL}
%	\postcode{60637}
	\country{USA}}
\email{ks@cs.uchicago.edu}

@@

\section{Implementation}
We are implementing QHTT in the F* programming language.

One issue with the original formulation of Hoare Type Theory is that using Hoare triples does not directly lead to a verification condition generation algorithm. This results in requiring a complicated bidirectional typing system for implementation. If we use predicate transformers as demonstrated by the use of Dijkstra monads in F*, we can avoid these issues \cite{swamy2013verifying}.

The current steps for the implementation are:

\begin{itemize}
	\item Design a memory model for representing quantum state, along with elementary operations such as read, write, lookup, etc
	\item Expose a new Quantum effect in F* by using the Dijkstra Monads for Free technique \cite{dm4free2017}.
	\item Port our language to work well with F* syntax.
\end{itemize}

This will necessarily take us away from the bidirectional typing approach used in the previous section. But the end result for the user would be the same. Indeed, F* system is an evolution of the HTT approach that comes with inherent support for effects and automation using an SMT solver.
